Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-29 wearables_survey.tex
part of results un-roughed. Still 4 sections to go.

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 464).

@@

\section{Results}
After removing X incomplete responses, our sample consisted of Y participants. Of these X, A\% were male, with a median age of B. Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

\subsection{Factors in Upsetting Users}
We found that the data type and data recipient, respectively, are the most significant predictors of how upsetting or threatening a situation is perceived by a user. On the other hand, the device type does not significantly impact how users perceive a situation.

Specifically, people are most upset about x, y, z, when shared with public, work, or friends.

People have different expectations of privacy when they perceive that data is being shared with an app rather than a human audience.

@@

\subsection{Correlation with Demographics}
Talk about if any of the results correlated with demographics here. go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape). There should be some interesting stuff there, whether there are specific correlations, or whether there is not. Both are good things to report and should be put here.

@@

\subsection{Perceived Concerns for Wearable Devices}
(REDO) Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices. Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.

(I should probably make a table of the following. Ugh, but for now:)

@@

Miscellaneous 		76 (4.26\%)\\
None				51 (2.86\%)\\
Don't know			 30 (1.68\%)\\
Don't care 			6 (0.34\%)\\

Talk about the coding labels and what they mean, in a very vague and compact way. Refer people to the appendix \ref{sec:coding} for what the coding means in detail.

Takeaway is that people care about privacy, then security, health, social impact. Other interesting things to note are aesthetics, social stigma, and false information, which could be cool things to look into.

@@

\subsection{What Matters in Upsetting People}
(REDO) Talk about the REGRESSION MODEL here. Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.

>>>>

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 465).

@@

\section{Results}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

Generally, any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deductible traits, such as the language being spoken, gender, and age, is considered the least sensitive.  Additionally, data shared in any way, whether the recipient be friends, work contacts, or the public, is much more upsetting than the data is only shared with an app's server; there is no statistically significant difference between how upset a person would be if data was shared between the various recipients. Interestingly, people had another set of prioritized concerns when data was perceived to be shared with an app rather than a human recipient (for instance, people were okay with people knowing if they were busy or not, but not their device). Although whether the device in the scenario being a wearable or smart phone did elicit unique reactions of the situation from participants, no statistically significant conclusion can be made about whether one device was seen as more threatening than another device.

People consider most things to be non-risky.

Self-reportedly, people are concerned about privacy.

@@

\subsection{Correlation with Demographics}
%I didn't do the correlation yet
We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).

%sentence for each factor and why it is/isn't correlated with the very upset rate; I just put in examples sentences here to fill it in; I will change them later. 
Because wearable devices have been adopted by a younger, rich, technology-savvy demographic  \cite{cmo}, it is natural to see that younger or more educated participants have had a more favorable view of wearable devices. This may be due to cultural exposure through marketing or friends, or an attitude of openness to new technologies. Participants who had a higher IUIPC score, which infers a higher sensitivity to privacy, were more likely to be upset at the various scenarios which may occur when wearing a wearable device. Additionally, these people were more likely to be adverse to these technologies for the sake of preserving privacy, whether they had explicit concerns or a vague feeling of uneasiness. There was no correlation between a person's gender and their views of wearable devices, reaffirming that wearable devices are equally exposed to both genders.

@@

\subsection{Perceived Concerns for Wearable Devices}
Near the end of the survey, we asked the participants an open-ended question, asking for the most likely risks associated with owning and interacting with wearable devices. Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:

@@

Miscellaneous 		76 (4.26\%)\\
None				51 (2.86\%)\\
Don't know		 30 (1.68\%)\\
Don't care 			6 (0.34\%)\\ [-.5cm]

Other significant secondary concerns included information compromise (Security), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

@@

\subsection{A Regression Model}
(REDO) Talk about the REGRESSION MODEL here. Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.
